---
title: "Untitled"
author: "Matthew Lam"
date: "2023-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data
```{r}
library(sp)
library(sf)
library(maptools)
library(tmap)
library(janitor)
library(tidyverse)
```

## Read in the fire data
```{r}
#read the fire points
setwd("~/Week 7 Task/MODIS_C6_1_Global_7d")
firepoints <- st_read("MODIS_C6_1_Global_7d.shp") # this is not a spatial points object 

#filter for 75% confidence and above
library(tidyverse)
firepoints75ci <- firepoints %>%filter(CONFIDENCE>=75)
plot(st_geometry(firepoints75ci))

#firepoints75ci <- st_transform(firepoints75ci, crs="ESRI:102038")
#plot(firepoints75ci)

```



##Now make a raster and basic plotting
```{r}
library(raster)
library(spatstat)
#first, set a window 
window <- as.owin(firepoints75ci$geometry)

#extract just the coordinates of the fire points
firepoints75ci_xy <- firepoints75ci %>% st_coordinates()

#then create a ppp object
firepoints75cippp <- ppp(x=firepoints75ci_xy[,1], y=firepoints75ci_xy[,2], window=window)

#inspect ppp object
plot(firepoints75cippp)


#check for duplicates
anyDuplicated(firepoints75cippp) #FALSE

#add a jitter
firepoints75cippp_jitter <- rjitter(firepoints75cippp, retry=TRUE, nsim=1,drop=TRUE )

plot(firepoints75cippp_jitter)


# now create a raster layer using kernel density estimation
library(raster)
kde_raster <- density.ppp(firepoints75cippp_jitter, sigma=0.3, edge=T) %>%
  raster()

plot(kde_raster)

#now set the crs for projecction 
crs(kde_raster) <- "+proj=longlat +datum=WGS84 +no_defs"

plot(kde_raster)


#using a sexier palette
library(viridis)
library(tmap)

tm_shape(kde_raster)+tm_raster("layer", palette="-magma", style="jenks")


#load in the basemap
basemap <- st_read("ne_10m_land.shp")
plot(basemap)


#set low values to NA
kde_raster[kde_raster < -1.992443e-14] <- NA
kde_raster[kde_raster <= 0.5] <- NA


#cropping the raster layer to our basemap
#now raster with basemap
tm_shape(kde_raster)+tm_raster("layer", palette="-magma", breaks=c(0,20,50,100,250,400))+
  tm_shape(basemap)+tm_borders(alpha=0.5, col="grey")+
  tm_layout(legend.outside = T, frame=F)

tm_shape(kde_raster)+tm_raster("layer", palette="-magma", style="jenks")+
  tm_shape(basemap)+tm_borders(alpha=0.5, col="grey")+
  tm_layout(legend.outside = T, frame=F)
#min 0.5041202
#max 382.787


df <- c(0.5:382)
quantile(df)
```

#now reprojecting
```{r}

library(sp)

kde_raster_reprojected <- projectRaster(kde_raster, crs=crs("+proj=ortho +lat_0=5 +lon_0=10"))

plot(kde_raster_reprojected)

library(rgdal)

# basemap2 <- readOGR("~/Week 7 Task","ne_10m_land")
# plot(basemap2)
# 
# library(sp)
# basemap_reprojected <- st_transform(st_as_sf(basemap2), "+proj=ortho +lat_0=2.231859 +lon_0=17.884319 +x_0=0 +y_0=0 +a=6370997 +b=6370997 +units=m +no_defs")
# 
# plot(st_geometry(basemap_reprojected))
# 
# basemap_reprojected2 <- basemap
# #basemap_reprojected2 <- as_Spatial(basemap_reprojected2)
# class(basemap_reprojected2)
# 
# 
# basemap_reprojected2 <- st_transform(basemap_reprojected2, "+proj=ortho +lat_0=2.231859 +lon_0=17.884319 +x_0=0 +y_0=0 +a=6370997 +b=6370997 +units=m +no_defs")
# 
# 
# st_crs(basemap_reprojected2)
# plot(basemap_reprojected2)
# 
# 
# tm_shape(kde_raster_reprojected)+tm_raster("layer", palette="-magma", style="jenks")+
#   tm_shape(basemap_reprojected)+tm_borders(alpha=1, col="grey")+
#   tm_layout(legend.outside = T, frame=F)
# 
# 
# tm_shape(basemap_reprojected2)+tm_fill()

```



## Trying reprojeciton with ggplot
```{r}
library(sf)
library(ggplot2)
library(mapview)
library(lwgeom)
library(rnaturalearth)

# world data
world <- rnaturalearth::ne_countries(scale = 'small', returnclass = 'sf')

# Fix polygons so they don't get cut in ortho projection
world  <- st_cast(world, 'MULTILINESTRING') %>%
  st_cast('LINESTRING', do_split=TRUE) %>%
  mutate(npts = npts(geometry, by_feature = TRUE)) %>%
  st_cast('POLYGON')

ggplot() +
  geom_sf(data=world, color="gray80", aes()) +
  coord_sf( crs= "+proj=ortho +lat_0=5 +lon_0=10")+
  theme_bw()


#make the raster an spdf
kde_raster_reprojected_spdf <- as(kde_raster_reprojected, "SpatialPixelsDataFrame")

kde_raster_reprojected_spdf<- as.data.frame(kde_raster_reprojected_spdf)

colnames(kde_raster_reprojected_spdf) <- c("value", "x", "y")


ggplot() +
  geom_sf(data=world, color="gray80", aes()) +
  coord_sf( crs= "+proj=ortho +lat_0=5 +lon_0=10")+
  geom_tile(data=kde_raster_reprojected_spdf, aes(x=x, y=y, fill=value),alpha=0.8)+
  scale_fill_viridis()
  theme_bw()

```


#reprojecting to winkeltriple
```{r}
#epsg: 5070
library(proj4)
library(PROJ)

#first reproject basemap
basemap_winkeltriple <- st_transform(basemap, crs="+proj=eck4 +lon_0=0 +x_0=0 +y_0=0 +R=6371000 +units=m +no_defs +type=crs")
plot(st_geometry(basemap_winkeltriple))

bcrs(basemap_winkeltriple)


#then reproject the raster
kde_raster_winkeltriple <- projectRaster(kde_raster, crs=crs("+proj=eck4 +lon_0=0 +x_0=0 +y_0=0 +R=6371000 +units=m +no_defs +type=crs"))
plot(kde_raster_winkeltriple)

tm_shape(kde_raster_winkeltriple)+tm_raster("layer", palette="-magma", breaks=c(0,20,50,100,250,400))+
  tm_shape(basemap_winkeltriple)+tm_borders(alpha=0.5, col="grey")+
  tm_layout(legend.outside = T, frame=F)
```

## Looping through the years
```{r}
setwd("/nfs/cfs/home3/zcfa/zcfamgl/Week 7 Task/fires points 2001to2010")


for(year in 2001:2010){
  assign(paste0("firepoints_",year), st_read(paste0(year,".shp")))

}






#now open the folder
setwd("/nfs/cfs/home3/zcfa/zcfamgl/Week 7 Task/fires points 2001to2010/fires2011to2021")
for(year in 2011:2021){
  assign(paste0("firepoints_",year), st_read(paste0(year,".shp")))
}

# #inspect
# firepoints_2001 %>% filter(CONFIDENCE>=75)

firepoints_2001 <- firepoints_2001 %>% filter(CONFIDENCE>=75)
firepoints_2002 <- firepoints_2002 %>% filter(CONFIDENCE>=75)
firepoints_2003 <- firepoints_2003 %>% filter(CONFIDENCE>=75)
firepoints_2004 <- firepoints_2004 %>% filter(CONFIDENCE>=75)
firepoints_2005 <- firepoints_2005 %>% filter(CONFIDENCE>=75)
firepoints_2006 <- firepoints_2006 %>% filter(CONFIDENCE>=75)
firepoints_2007 <- firepoints_2007 %>% filter(CONFIDENCE>=75)
firepoints_2008 <- firepoints_2008 %>% filter(CONFIDENCE>=75)
firepoints_2009 <- firepoints_2009 %>% filter(CONFIDENCE>=75)
firepoints_2010 <- firepoints_2010 %>% filter(CONFIDENCE>=75)
firepoints_2011 <- firepoints_2011 %>% filter(CONFIDENCE>=75)
firepoints_2012 <- firepoints_2012 %>% filter(CONFIDENCE>=75)
firepoints_2013 <- firepoints_2013 %>% filter(CONFIDENCE>=75)
firepoints_2014 <- firepoints_2014 %>% filter(CONFIDENCE>=75)
firepoints_2015 <- firepoints_2015 %>% filter(CONFIDENCE>=75)
firepoints_2016 <- firepoints_2016 %>% filter(CONFIDENCE>=75)
firepoints_2017 <- firepoints_2017 %>% filter(CONFIDENCE>=75)
firepoints_2018 <- firepoints_2018 %>% filter(CONFIDENCE>=75)
firepoints_2019 <- firepoints_2019 %>% filter(CONFIDENCE>=75)
firepoints_2020 <- firepoints_2020 %>% filter(CONFIDENCE>=75)
firepoints_2021 <- firepoints_2021 %>% filter(CONFIDENCE>=75)

plot(st_geometry(firepoints_2012))
plot(st_geometry(firepoints_2021))

```

##MAKE A RASTER
```{r}
library(raster)
library(spatstat)
#first, set a window 
window <- as.owin(firepoints_2001$geometry)
#extract just the coordinates of the fire points
firepoints_2001_xy <- firepoints_2001 %>% st_coordinates()
#then create a ppp object
firepoints_2001ppp <- ppp(x=firepoints_2001_xy[,1], y=firepoints_2001_xy[,2], window=window)
#add a jitter
firepoints_2001ppp_jitter <- rjitter(firepoints_2001ppp, retry=TRUE, nsim=1,drop=TRUE )
# now create a raster layer using kernel density estimation
library(raster)
raster_firepoints_2001 <- density.ppp(firepoints_2001ppp_jitter, sigma=1, edge=T) %>%
  raster()
plot(raster_firepoints_2001)
#now set the crs for projecction 
crs(raster_firepoints_2001) <-  "+proj=longlat +datum=WGS84 +no_defs"
plot(raster_firepoints_2001)
#set low values to NA
raster_firepoints_2001[raster_firepoints_2001 < -1.992443e-14] <- NA
raster_firepoints_2001[raster_firepoints_2001 <= 0.5] <- NA
#reprojection
raster_firepoints_2001 <- projectRaster(raster_firepoints_2001, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```





##READ IN SOUTH AMERICA
```{r}
southamericashape <- st_read("SouthAmerica.shp")
plot(st_geometry(southamericashape))

#set projectoin
southamericashape <- st_transform(southamericashape,crs="+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs" )
plot(st_geometry(southamericashape))

southamericashape <- st_make_valid(southamericashape)
tm_shape(southamericashape)+tm_borders(alpha=0.5, col="grey")

```


##NOW IN TMAP
```{r}
sunsetpal <- c("#fcde9c","#faa476","#f0746e","#e34f6f","#dc3977","#b9257a","#7c1d6f")

sunsetpal2 <- c("#ecda9a","#efc47e","#f3ad6a","#f7945d","#f97b57","#f66356","#ee4d5a")


tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2001)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)
```

## 2002 raster
```{r}
#2002
window <- as.owin(firepoints_2002$geometry)

firepoints_2002_xy <- firepoints_2002 %>% st_coordinates()

firepoints_2002ppp <- ppp(x=firepoints_2002_xy[,1], y=firepoints_2002_xy[,2], window=window)

firepoints_2002ppp_jitter <- rjitter(firepoints_2002ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2002 <- density.ppp(firepoints_2002ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2002) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2002)

raster_firepoints_2002[raster_firepoints_2002 < -1.992443e-14] <- NA

raster_firepoints_2002[raster_firepoints_2002 <= 0.5] <- NA

raster_firepoints_2002 <- projectRaster(raster_firepoints_2002, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


## 2003 raster
```{r}
window <- as.owin(firepoints_2003$geometry)

firepoints_2003_xy <- firepoints_2003 %>% st_coordinates()

firepoints_2003ppp <- ppp(x=firepoints_2003_xy[,1], y=firepoints_2003_xy[,2], window=window)

firepoints_2003ppp_jitter <- rjitter(firepoints_2003ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2003 <- density.ppp(firepoints_2003ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2003) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2003)

raster_firepoints_2003[raster_firepoints_2003 < -1.992443e-14] <- NA

raster_firepoints_2003[raster_firepoints_2003 <= 0.5] <- NA

raster_firepoints_2003 <- projectRaster(raster_firepoints_2003, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```

## 2004 raster
```{r}
window <- as.owin(firepoints_2004$geometry)

firepoints_2004_xy <- firepoints_2004 %>% st_coordinates()

firepoints_2004ppp <- ppp(x=firepoints_2004_xy[,1], y=firepoints_2004_xy[,2], window=window)

firepoints_2004ppp_jitter <- rjitter(firepoints_2004ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2004 <- density.ppp(firepoints_2004ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2004) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2004)

raster_firepoints_2004[raster_firepoints_2004 < -1.992443e-14] <- NA

raster_firepoints_2004[raster_firepoints_2004 <= 0.5] <- NA

raster_firepoints_2004 <- projectRaster(raster_firepoints_2004, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


## 2005 raster
```{r}
window <- as.owin(firepoints_2005$geometry)

firepoints_2005_xy <- firepoints_2005 %>% st_coordinates()

firepoints_2005ppp <- ppp(x=firepoints_2005_xy[,1], y=firepoints_2005_xy[,2], window=window)

firepoints_2005ppp_jitter <- rjitter(firepoints_2005ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2005 <- density.ppp(firepoints_2005ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2005) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2005)

raster_firepoints_2005[raster_firepoints_2005 < -1.992443e-14] <- NA

raster_firepoints_2005[raster_firepoints_2005 <= 0.5] <- NA

raster_firepoints_2005 <- projectRaster(raster_firepoints_2005, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


## 2006 raster
```{r}
window <- as.owin(firepoints_2006$geometry)

firepoints_2006_xy <- firepoints_2006 %>% st_coordinates()

firepoints_2006ppp <- ppp(x=firepoints_2006_xy[,1], y=firepoints_2006_xy[,2], window=window)

firepoints_2006ppp_jitter <- rjitter(firepoints_2006ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2006 <- density.ppp(firepoints_2006ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2006) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2006)

raster_firepoints_2006[raster_firepoints_2006 < -1.992443e-14] <- NA

raster_firepoints_2006[raster_firepoints_2006 <= 0.5] <- NA

raster_firepoints_2006 <- projectRaster(raster_firepoints_2006, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```



## 2007 raster
```{r}
window <- as.owin(firepoints_2007$geometry)

firepoints_2007_xy <- firepoints_2007 %>% st_coordinates()

firepoints_2007ppp <- ppp(x=firepoints_2007_xy[,1], y=firepoints_2007_xy[,2], window=window)

firepoints_2007ppp_jitter <- rjitter(firepoints_2007ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2007 <- density.ppp(firepoints_2007ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2007) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2007)

raster_firepoints_2007[raster_firepoints_2007 < -1.992443e-14] <- NA

raster_firepoints_2007[raster_firepoints_2007 <= 0.5] <- NA

raster_firepoints_2007 <- projectRaster(raster_firepoints_2007, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```

## 2008 raster
```{r}
window <- as.owin(firepoints_2008$geometry)

firepoints_2008_xy <- firepoints_2008 %>% st_coordinates()

firepoints_2008ppp <- ppp(x=firepoints_2008_xy[,1], y=firepoints_2008_xy[,2], window=window)

firepoints_2008ppp_jitter <- rjitter(firepoints_2008ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2008 <- density.ppp(firepoints_2008ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2008) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2008)

raster_firepoints_2008[raster_firepoints_2008 < -1.992443e-14] <- NA

raster_firepoints_2008[raster_firepoints_2008 <= 0.5] <- NA

raster_firepoints_2008 <- projectRaster(raster_firepoints_2008, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


## 2009 raster
```{r}
window <- as.owin(firepoints_2009$geometry)

firepoints_2009_xy <- firepoints_2009 %>% st_coordinates()

firepoints_2009ppp <- ppp(x=firepoints_2009_xy[,1], y=firepoints_2009_xy[,2], window=window)

firepoints_2009ppp_jitter <- rjitter(firepoints_2009ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2009 <- density.ppp(firepoints_2009ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2009) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2009)

raster_firepoints_2008[raster_firepoints_2009 < -1.992443e-14] <- NA

raster_firepoints_2009[raster_firepoints_2009 <= 0.5] <- NA

raster_firepoints_2009 <- projectRaster(raster_firepoints_2009, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```



## 2010 raster
```{r}
window <- as.owin(firepoints_2010$geometry)

firepoints_2010_xy <- firepoints_2010 %>% st_coordinates()

firepoints_2010ppp <- ppp(x=firepoints_2010_xy[,1], y=firepoints_2010_xy[,2], window=window)

firepoints_2010ppp_jitter <- rjitter(firepoints_2010ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2010 <- density.ppp(firepoints_2010ppp_jitter, sigma=1, edge=T) %>%
  raster()

crs(raster_firepoints_2010) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2010)

raster_firepoints_2010[raster_firepoints_2010 < -1.992443e-14] <- NA

raster_firepoints_2010[raster_firepoints_2010 <= 0.5] <- NA

raster_firepoints_2010 <- projectRaster(raster_firepoints_2010, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```



##2011
```{r}
#2011

window <- as.owin(firepoints_2011$geometry)

 

firepoints_2011_xy <- firepoints_2011 %>% st_coordinates()

 

firepoints_2011ppp <- ppp(x=firepoints_2011_xy[,1], y=firepoints_2011_xy[,2], window=window)

 

firepoints_2011ppp_jitter <- rjitter(firepoints_2011ppp, retry=TRUE, nsim=1,drop=TRUE )

 

raster_firepoints_2011 <- density.ppp(firepoints_2011ppp_jitter, sigma=1, edge=T) %>%

  raster()

 

crs(raster_firepoints_2011) <-  "+proj=longlat +datum=WGS84 +no_defs"

 

plot(raster_firepoints_2011)

 

raster_firepoints_2011[raster_firepoints_2011 < -1.992443e-14] <- NA

 

raster_firepoints_2011[raster_firepoints_2011 <= 0.5] <- NA

 

raster_firepoints_2011 <- projectRaster(raster_firepoints_2011, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```

##2012
```{r}
#2012

window <- as.owin(firepoints_2012$geometry)

firepoints_2012_xy <- firepoints_2012 %>% st_coordinates()

firepoints_2012ppp <- ppp(x=firepoints_2012_xy[,1], y=firepoints_2012_xy[,2], window=window)

firepoints_2012ppp_jitter <- rjitter(firepoints_2012ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2012 <- density.ppp(firepoints_2012ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2012) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2012) 

raster_firepoints_2012[raster_firepoints_2012 < -1.992443e-14] <- NA

raster_firepoints_2012[raster_firepoints_2012 <= 0.5] <- NA
 

raster_firepoints_2012 <- projectRaster(raster_firepoints_2012, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```

##2013
```{r}
#2013

window <- as.owin(firepoints_2013$geometry)

firepoints_2013_xy <- firepoints_2013 %>% st_coordinates()

firepoints_2013ppp <- ppp(x=firepoints_2013_xy[,1], y=firepoints_2013_xy[,2], window=window)

firepoints_2013ppp_jitter <- rjitter(firepoints_2013ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2013 <- density.ppp(firepoints_2013ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2013) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2013) 

raster_firepoints_2013[raster_firepoints_2013 < -1.992443e-14] <- NA

raster_firepoints_2013[raster_firepoints_2013 <= 0.5] <- NA
 

raster_firepoints_2013 <- projectRaster(raster_firepoints_2013, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


##2014
```{r}
#2014

window <- as.owin(firepoints_2014$geometry)

firepoints_2014_xy <- firepoints_2014 %>% st_coordinates()

firepoints_2014ppp <- ppp(x=firepoints_2014_xy[,1], y=firepoints_2014_xy[,2], window=window)

firepoints_2014ppp_jitter <- rjitter(firepoints_2014ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2014 <- density.ppp(firepoints_2014ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2014) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2014) 

raster_firepoints_2014[raster_firepoints_2014 < -1.992443e-14] <- NA

raster_firepoints_2014[raster_firepoints_2014 <= 0.5] <- NA

raster_firepoints_2014 <- projectRaster(raster_firepoints_2014, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```





##2015
```{r}
#2015

window <- as.owin(firepoints_2015$geometry)

firepoints_2015_xy <- firepoints_2015 %>% st_coordinates()

firepoints_2015ppp <- ppp(x=firepoints_2015_xy[,1], y=firepoints_2015_xy[,2], window=window)

firepoints_2015ppp_jitter <- rjitter(firepoints_2015ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2015 <- density.ppp(firepoints_2015ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2015) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2015)

raster_firepoints_2015[raster_firepoints_2015 < -1.992443e-14] <- NA

raster_firepoints_2015[raster_firepoints_2015 <= 0.5] <- NA

raster_firepoints_2015 <- projectRaster(raster_firepoints_2015, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


##2016
```{r}
#2016

window <- as.owin(firepoints_2016$geometry)

firepoints_2016_xy <- firepoints_2016 %>% st_coordinates()

firepoints_2016ppp <- ppp(x=firepoints_2016_xy[,1], y=firepoints_2016_xy[,2], window=window)

firepoints_2016ppp_jitter <- rjitter(firepoints_2016ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2016 <- density.ppp(firepoints_2016ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2016) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2016)

raster_firepoints_2016[raster_firepoints_2016 < -1.992443e-14] <- NA

raster_firepoints_2016[raster_firepoints_2016 <= 0.5] <- NA

raster_firepoints_2016 <- projectRaster(raster_firepoints_2016, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


##2017
```{r}
#2017

window <- as.owin(firepoints_2017$geometry)

firepoints_2017_xy <- firepoints_2017 %>% st_coordinates()

firepoints_2017ppp <- ppp(x=firepoints_2017_xy[,1], y=firepoints_2017_xy[,2], window=window)

firepoints_2017ppp_jitter <- rjitter(firepoints_2017ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2017 <- density.ppp(firepoints_2017ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2017) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2017)

raster_firepoints_2017[raster_firepoints_2017 < -1.992443e-14] <- NA

raster_firepoints_2017[raster_firepoints_2017 <= 0.5] <- NA

raster_firepoints_2017 <- projectRaster(raster_firepoints_2017, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


##2018
```{r}
#2018

window <- as.owin(firepoints_2018$geometry)

firepoints_2018_xy <- firepoints_2018 %>% st_coordinates()

firepoints_2018ppp <- ppp(x=firepoints_2018_xy[,1], y=firepoints_2018_xy[,2], window=window)

firepoints_2018ppp_jitter <- rjitter(firepoints_2018ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2018 <- density.ppp(firepoints_2018ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2018) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2018)

raster_firepoints_2018[raster_firepoints_2018 < -1.992443e-14] <- NA

raster_firepoints_2018[raster_firepoints_2018 <= 0.5] <- NA

raster_firepoints_2018 <- projectRaster(raster_firepoints_2018, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```


##2019
```{r}
#2019

window <- as.owin(firepoints_2019$geometry)

firepoints_2019_xy <- firepoints_2019 %>% st_coordinates()

firepoints_2019ppp <- ppp(x=firepoints_2019_xy[,1], y=firepoints_2019_xy[,2], window=window)

firepoints_2019ppp_jitter <- rjitter(firepoints_2019ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2019 <- density.ppp(firepoints_2019ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2019) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2019)

raster_firepoints_2019[raster_firepoints_2019 < -1.992443e-14] <- NA

raster_firepoints_2019[raster_firepoints_2019 <= 0.5] <- NA

raster_firepoints_2019 <- projectRaster(raster_firepoints_2019, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))

```

##2020
```{r}
#2020

window <- as.owin(firepoints_2020$geometry)

firepoints_2020_xy <- firepoints_2020 %>% st_coordinates()

firepoints_2020ppp <- ppp(x=firepoints_2020_xy[,1], y=firepoints_2020_xy[,2], window=window)

firepoints_2020ppp_jitter <- rjitter(firepoints_2020ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2020 <- density.ppp(firepoints_2020ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2020) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2020)

raster_firepoints_2020[raster_firepoints_2020 < -1.992443e-14] <- NA

raster_firepoints_2020[raster_firepoints_2020 <= 0.5] <- NA

raster_firepoints_2020 <- projectRaster(raster_firepoints_2020, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```

##2021
```{r}
#2021

window <- as.owin(firepoints_2021$geometry)

firepoints_2021_xy <- firepoints_2021 %>% st_coordinates()

firepoints_2021ppp <- ppp(x=firepoints_2021_xy[,1], y=firepoints_2021_xy[,2], window=window)

firepoints_2021ppp_jitter <- rjitter(firepoints_2021ppp, retry=TRUE, nsim=1,drop=TRUE )

raster_firepoints_2021 <- density.ppp(firepoints_2021ppp_jitter, sigma=1, edge=T) %>%raster()

crs(raster_firepoints_2021) <-  "+proj=longlat +datum=WGS84 +no_defs"

plot(raster_firepoints_2021)

raster_firepoints_2021[raster_firepoints_2021 < -1.992443e-14] <- NA

raster_firepoints_2021[raster_firepoints_2021 <= 0.5] <- NA

raster_firepoints_2021 <- projectRaster(raster_firepoints_2021, crs=crs("+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs +type=crs"))
```




#maps for every year
```{r}
m01 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2001)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m02 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2002)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m03 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2003)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m04 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2004)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m05 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2005)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m06 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2006)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m07 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2007)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m08 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2008)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m09 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2009)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m10 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2010)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m11 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2011)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m12 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2012)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m13 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2013)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m14 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2014)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m15 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2015)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m16 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2016)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m17 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2017)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m18 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2018)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m19 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2019)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m20 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2020)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)

m21 <- tm_shape(southamericashape)+tm_borders(alpha=0, col="transparent")+
  tm_shape(raster_firepoints_2021)+tm_raster("layer",palette=sunsetpal2, style="fisher", legend.show=F)+
  tm_shape(southamericashape)+tm_borders(alpha=0.5, col="black")+
  tm_layout(frame=F)


```
##SAVE TMAPS
```{r}
setwd("/nfs/cfs/home3/zcfa/zcfamgl/Week 7 Task/tmap_outputs")
tmap_save(m01, "m01.pdf")
tmap_save(m02, "m02.pdf")
tmap_save(m03, "m03.pdf")
tmap_save(m04, "m04.pdf")
tmap_save(m05, "m05.pdf")
tmap_save(m06, "m06.pdf")
tmap_save(m07, "m07.pdf")
tmap_save(m08, "m08.pdf")
tmap_save(m09, "m09.pdf")
tmap_save(m10, "m10.pdf")
tmap_save(m11, "m11.pdf")
tmap_save(m12, "m12.pdf")
tmap_save(m13, "m13.pdf")
tmap_save(m14, "m14.pdf")
tmap_save(m15, "m15.pdf")
tmap_save(m16, "m16.pdf")
tmap_save(m17, "m17.pdf")
tmap_save(m18, "m18.pdf")
tmap_save(m19, "m19.pdf")
tmap_save(m20, "m20.pdf")
tmap_save(m21, "m21.pdf")

tmap_arrange(m01,m02,m03,m04,m05,m06,m07,m08,m09,m10,m11,m12,m13,m14,m15,m16,m17,m18,m19,m20,nrow=5,ncol=4)

```

## and then as pngs in case it's too large for illustrator
```{r}
setwd("/nfs/cfs/home3/zcfa/zcfamgl/Week 7 Task/tmap_outputs")
tmap_save(m01, "m01.png")
tmap_save(m02, "m02.png")
tmap_save(m03, "m03.png")
tmap_save(m04, "m04.png")
tmap_save(m05, "m05.png")
tmap_save(m06, "m06.png")
tmap_save(m07, "m07.png")
tmap_save(m08, "m08.png")
tmap_save(m09, "m09.png")
tmap_save(m10, "m10.png")
tmap_save(m11, "m11.png")
tmap_save(m12, "m12.png")
tmap_save(m13, "m13.png")
tmap_save(m14, "m14.png")
tmap_save(m15, "m15.png")
tmap_save(m16, "m16.png")
tmap_save(m17, "m17.png")
tmap_save(m18, "m18.png")
tmap_save(m19, "m19.png")
tmap_save(m20, "m20.png")
tmap_save(m21, "m21.png")
```


