---
title: "Untitled"
author: "Matthew Lam"
date: "2023-02-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HDX API Setup
```{r}
# library(remotes)
# remotes::install_gitlab("dickoa/rhdx")
library(rhdx)

#connecting to prod db
set_rhdx_config(hdx_site="prod")
get_rhdx_config()
```


## Getting Turkey admin boundaries Data
```{r}
#libraries
library(sf)
library(sp)
library(tidyverse)
library(tmap)

#read manually
turkeyadminboundaries <- read_sf("tur_polbna_adm2.shp")

#baseplot
plot(st_geometry(turkeyadminboundaries))
```

## load hex
```{r}
biggesthex <- read_sf("biggesthex.shp")
medhex <- read_sf("mediumhex.shp")
smallhex <- read_sf("hex0.2.shp")
smallesthex <- read_sf("smallhex.shp")

plot(st_geometry(biggesthex))
plot(st_geometry(medhex))
plot(st_geometry(smallhex))
plot(st_geometry(smallesthex))
```

## get population data from hdx
```{r}
#search + pull + load data from hdx
turkeypopulation <- search_datasets("Türkiye - Subnational Population Statistics") %>% pluck(1) %>% get_resource(4) %>% read_resource(download_folder=tempdir()) %>% select(year, ADM2_EN, ADM2_PCODE, T_TL) #again! SO DAMN CLEAN <333

turkeypopulation 
```

## pop to hex
```{r}
#configure small hex
#coeerce from sf to sp object
smallhex_df <- as_Spatial(smallhex)
class(smallhex_df)


#basic hex plot
ggplot()+
  geom_polygon(data=smallhex_df, aes(x=long, y=lat, group=group), fill="skyblue", color="white")+theme_void()+coord_map()
```


# Pull Turkey Heatlh Points
```{r}
turkeyhealthpoints <- search_datasets("HOTOSM Turkey Health Facilities (OpenStreetMap Export)") %>% pluck(1) %>% get_resource(1) %>% read_resource(download_folder=tempdir()) 

plot(st_geometry(turkeyhealthpoints))

st_coordinates(turkeyhealthpoints)
```


## Point in polygon to get healthcare facilities per pop
```{r}
#stmakegrid
grid <- st_make_grid(turkeyadminboundaries, what="polygons", square=FALSE, cellsize=0.6)


#first, get population 
turkeypopadmin_spdf <- left_join(turkeyadminboundaries, turkeypopulation, by=c("pcode"= "ADM2_PCODE"))
turkeypopadmin_spdf <- as_Spatial(turkeypopadmin_spdf)
turkeypopadmin_spdf@data$T_TL <- as.numeric(turkeypopadmin_spdf@data$T_TL)

#fortify? 
library(broom)
turkeypopadmin_spdf_fortified <- tidy(turkeypopadmin_spdf, region ="pcode")

#join again after fortification 
turkeypopadmin_spdf_fortified <- turkeypopadmin_spdf_fortified %>% left_join(., turkeypopulation, by=c("id"="ADM2_PCODE"))


pal <- c("#fde0c5","#facba6","#f8b58b","#f59e72","#f2855d","#ef6a4c","#eb4a40")


#transform points into spatial points
plot(turkeyhealthpoints)
st_crs(turkeyhealthpoints)
turkeyhealthpoints_df <- as.data.frame(st_coordinates(turkeyhealthpoints))
  
#simple map
library(viridis)
ggplot()+
  geom_polygon(data=turkeypopadmin_spdf_fortified, aes(x=long, y=lat, group=group, fill=T_TL))+
  theme_void()+
  scale_fill_viridis(name="Population")+
  geom_point(data=turkeyhealthpoints_df,aes(x=X, y=Y), col="red")+
  coord_map()




## point in polygon! 
class(turkeyhealthpoints)
turkeyhealthpoints_spdf <- as_Spatial(turkeyhealthpoints)
res <- over(turkeyhealthpoints_spdf, turkeypopadmin_spdf)
a<- table(res$pcode)
a_df <- data.frame(rbind(a))
point_in_poly_count <- gather(a_df, pcode, count_health_facilities, TUR001002:TUR081008, factor_key=T)


#merge point in poly count back into the admin boundaries
df2 <- merge(turkeypopadmin_spdf_fortified, point_in_poly_count, by.x="id", by.y="pcode")
df2$health_per_capita <- (df2$count_health_facilities/df2$T_TL.x)
df2$health_per_100000 <- df2$health_per_capita * 100000


#plotting

#define the theme
theme_map <- function(...) {
  theme_minimal() +
  theme(
    text = element_text(family = "Ubuntu Regular", color = "#22211d"),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # panel.grid.minor = element_line(color = "#ebebe5", size = 0.2),
    panel.grid.major = element_line(color = "#ebebe5", size = 0.2),
    panel.grid.minor = element_blank(),
    plot.background = element_rect(fill = "#f5f5f2", color = NA), 
    panel.background = element_rect(fill = "#f5f5f2", color = NA), 
    legend.background = element_rect(fill = "#f5f5f2", color = NA),
    panel.border = element_blank(),
    ...
  )
}

library(ggthemes)
pretty_breaks <- c(0.5,7.3,16.8,28.1,128.8)
#find extremes
minVal <- min(df2$health_per_100000, na.rm = T)
maxVal <- max(df2$health_per_100000, na.rm = T)

#compute labels
labels <- c()
brks <- c(minVal, pretty_breaks, maxVal)
# round the labels (actually, only the extremes)
for(idx in 1:length(brks)){
  labels <- c(labels,round(brks[idx + 1], 2))
}
labels <- labels[1:length(labels)-1]


#define a new variable in the dataset just as above
df2$brks <- cut(df2$health_per_100000,
                breaks=brks,
                include.lowest=TRUE,
                labels=labels)


#get scales
brks_scale <- levels(df2$brks)
labels_scale <- rev(brks_scale)


p <- ggplot()+
  geom_polygon(data=df2, aes(fill=health_per_100000, 
                             x=long, 
                             y=lat, 
                             group=group))+
  geom_path(data=turkeypopadmin_spdf_fortified , aes(x=long, 
                          y=lat, 
                          group=group), 
            color="black", size=0.1)+
  coord_equal()+
  theme_map()+
  labs(x=NULL, 
       y=NULL, 
       title="Healthcare Facilities per 100000 People")+
  scale_fill_viridis(option = "magma", direction = -1)

p
```


## polygons to hexagons
```{r}

library(grid)
g <- st_make_grid(turkeyadminboundaries, square=FALSE)



ig = lengths(st_intersects(g, turkeyadminboundaries)) >0


plot(st_geometry(turkeyadminboundaries))
plot(g[ig], col="red", add=TRUE)
```

## a tmap approach
```{r}
library(tmap)
library(janitor)
library(tidyverse)
library(sp)
library(sf)




#using tmap
pal <- c("#fde0c5","#facba6","#f8b58b","#f59e72","#f2855d","#ef6a4c","#eb4a40")

pal2 <- c("#d2fbd4","#a5dbc2","#7bbcb0","#559c9e","#3a7c89","#235d72","#123f5a")




#clean up df2
df2 <- df2 %>% group_by(id) %>% select(id,count_health_facilities, health_per_100000, T_TL.x)
df2 <- unique(df2)

df2_sdf <- left_join(turkeyadminboundaries,df2, by=c("pcode"="id"))
#get NAs to 0
df2_sdf$health_per_100000[is.na(df2_sdf$health_per_100000)] <- 0
df2_sdf <- st_as_sf(df2_sdf)
class(df2_sdf)

#map inspection
tmap_mode("view")
tm_shape(turkeyadminboundaries)+tm_polygons("gray", border.col="white")+
  tm_shape(df2_sdf)+
  tm_polygons(col="health_per_100000", n=5, style="jenks", palette=pal2,)+
  tm_layout(legend.outside=TRUE, 
            legend.outside.position="right")


#creating dots in polygon for health per 1000000
num.dots <- as.data.frame(select(df2_sdf, health_per_100000))

library(maptools)
library(rgeos)
library(tidyverse)
library(rgdal)
library(ggthemes)


#create a dot in polygon which corresponds to the healthcarefacilities per 100,000 so that we can count again in the hexagons. 
sp.dfs <- lapply(names(num.dots)[1], function(x) {
  dotsInPolys(turkeyadminboundaries, as.integer(num.dots[, x]), f="random")
})


#make this a spatial obejct
df2_spdf <- as_Spatial(df2_sdf)

#create thd dots and assign into df2_spdf. CAll this a new object called healthper100000 points. 
healthper100000points <- dotsInPolys(df2_spdf, as.integer(df2_sdf$health_per_100000), f="random")
```




## now with hexagons
```{r}
library(rgeos)

#make hexagons using the geometry of turkeyhealthpoints, with cellsize 0.2. 
area_honeycomb_grid <- st_make_grid(st_geometry(turkeyhealthpoints), c(150,150), what="polygons", square=FALSE, cellsize=.2)
#inspect
plot(area_honeycomb_grid)


#to sf and add grid ID
honeycomb_grid_sf <- st_sf(area_honeycomb_grid)%>%
  mutate(grid_id = 1:length(lengths(area_honeycomb_grid)))

#make this an sf object to work with st_intersects() and friends. 
healthper100000points <- st_as_sf(healthper100000points)

#align the crs with the grid
st_crs(healthper100000points) = st_crs(honeycomb_grid_sf)

#point in poly count
honeycomb_grid_sf$healthper100000 <- lengths(st_intersects(honeycomb_grid_sf, st_geometry(healthper100000points))) 


                                                  
# remove grid without value of 0 (i.e. no points in side that grid)
honeycomb_count = filter(honeycomb_grid_sf, lengths(st_intersects(honeycomb_grid_sf, st_geometry(turkeyadminboundaries)))>0)

pal2 <- c("#f7feae","#b7e6a5","#7ccba2","#46aea0","#089099","#235d72","#123f5a")
pal4 <- c("#fcde9c","#faa476","#f0746e","#e34f6f","#dc3977","#b9257a","#7c1d6f")
pal3 <- c("#f3cbd3","#eaa9bd","#dd88ac","#ca699d","#b14d8e","#91357d","#6c2167")
teal <- c("#d1eeea","#a8dbd9","#85c4c9","#68abb8","#4f90a6","#3b738f","#2a5674")



                                                  
#mapping
tmap_mode("view")
tm_shape(honeycomb_count)+
  tm_fill(col="healthper100000",
          palette="-magma",
          style="jenks",
          n=6,
          id="grid_id", 
          showNA=FALSE, 
          alpha=0.6)+
  tm_borders(col="grey40", lwd=0.7)+
  tm_layout(frame=F, legend.outside=T)

#write to shapefile and continue in blender
 st_write(honeycomb_count, dsn=".", layer = "hexagons", driver= "ESRI Shapefile")
```



## Now in Mapdeck <- mapdeck doesn't have good customisability 
```{r}
library(mapdeck)

key <- "pk.eyJ1IjoibWF0dGhld2dhcmV0aGxhbSIsImEiOiJjbGI2eWp4NTUwNXgyM3dsamR6YjlvNjI5In0.UJBDZgX18UTqNg64t4e41A"

mapdeck(style = 'mapbox://styles/mapbox/dark-v9')


df <- read.csv(paste0(
  'https://raw.githubusercontent.com/uber-common/deck.gl-data/master/examples/'
  , '3d-heatmap/heatmap-data.csv'
))

df <- df[!is.na(df$lng), ]

df$e <- sample(100, size = nrow(df), replace = TRUE)

mapdeck( style = mapdeck_style("streets"), pitch = 45) %>%
  add_hexagon(
    data = df[ df$lat > 54.5, ]
    , lat = "lat"
    , lon = "lng"
    , layer_id = "hex_layer"
    , elevation_scale = 50
    , elevation="e"
    , colour_range = colourvalues::colour_values(1:6, palette = colourvalues::get_palette("viridis")[70:256,])
  )


mapdeck(style=mapdeck_style("dark"), pitch=45)%>%
  add_hexagon(
    data=honeycomb_count 
    ,layer="hex_layer"
    , elevation= "healthper100000"
    , elevation_scale=10
    
  )
```




## Mapdeck polygons <- but doesn't look good
```{r}
library(sf)
library(geojsonsf)

sf <- geojson_sf("https://symbolixau.github.io/data/geojson/SA2_2016_VIC.json")
sf$e <- sf$AREASQKM16 * 10 

mapdeck(token = key, style = mapdeck_style("dark"), pitch=45) %>%
  add_polygon(
    data = honeycomb_count
    , layer = "polygon_layer"
    , fill_colour = "healthper100000"
    , elevation = "healthper100000"
    , elevation_scale=100
    , palette = "ylorbr"
  )
``` 





## Read in the shapefile for globe
```{r}
worldraw <- st_read("~/OneDrive - University College London/Y3/Cartography and Data Visualisation/Week 6 Task/ne_10m_admin_0_countries/ne_10m_admin_0_countries.shp")

plot(worldraw)


#reprojecting to world from space
worldreprojected <- st_transform(worldraw, crs="ESRI:102038")


#now recenter
proj2 <- st_transform(worldraw,"+proj=ortho +lat_0=39.233288 +lon_0=35.725534 +x_0=0 +y_0=0 +ellps=sphere +units=m +no_defs")# 39.233288, 35.725534

plot(st_geometry(worldreprojected))
plot(st_geometry(proj2))
proj2 <- st_as_sf(proj2)

#get turkey
library(tidyverse)
turkey <- proj2 %>% filter(ADMIN=="Turkey")
plot(st_geometry(turkey))

```









